Processing large surveys with package MRP-KIT

### 2021-07-04 case-study/Munging_CCES.Rmd
added styling

---
title: "Processing large surveys with package MRP-KIT"
author: "Mitzi Morris"
output:
  html_document:
    toc: true
    toc_depth: 2
---

@@

### Survey data: the 2018 CCES Common Content Dataset

@@

### Population data:  the 2018 American Community Survey

@@

#### Inspecting the ACS sample

@@

### Aligning the survey and target population data with MRP-KIT

@@

#### Simple one-to-one mapping:  CCES "gender" / ACS "sex"

@@

#### One-to-one mapping over many labels: state of residence, 51 categories

@@

#### Choice of mapping: education

@@

#### Survey variable cannot be mapped to single census variable:  Race

@@

#### Many-to-many mapping: marital status

@@

#### Measurement recorded in different units and not binned:  age

@@

Choosing the former will result in more postratification cells (57% more, to be precise).

### Mapping the survey and target population data with MRP-KIT

We now have mappings for our 6 postratification variables:
`q_sex`, `q_state`, `q_educ`, `q_race`, `q_marstat`, `q_age`;
allowing for (at least) `2 * 51 * 6 * 8 * 6 * 4`  possible subsets of interest.

>>>>

---
title: "Processing large surveys with package MRP-KIT"
author: "Mitzi Morris"
output:
  rmdformats::robobook
---

@@

# Survey data: the 2018 CCES Common Content Dataset

@@

# Population data:  the 2018 American Community Survey

@@

## Inspecting the ACS sample

@@

# Aligning the survey and target population data with MRP-KIT

@@

## Simple one-to-one mapping:  CCES "gender" / ACS "sex"

@@

## One-to-one mapping over many labels: state of residence, 51 categories

@@

## Choice of mapping: education

@@

## Survey variable cannot be mapped to single census variable:  Race

@@

## Many-to-many mapping: marital status

@@

## Measurement recorded in different units and not binned:  age

@@

## Possible subpopulations of interest

The size of the postratification table is the product of the number of categories per demographic.
The more fine-grained the classification, the larger the postratification table.
In this example, we have variables:
`q_sex` (2 values), `q_state` (51 values), `q_educ` (6 values), `q_race` (8 values), `q_marstat` (5 values), `q_age` (many possible values - e.g. 4 or 7).
The resultng poststratification table will have at least 97,920 cells.

# Mapping the survey and target population data with MRP-KIT
